PRFDN: Reparameterize and Prune Disentangled U-Net for Efficient Image Super-resolution

### 2023-04-05 NTIRE 2023 Efficient SR Challenge Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

@@

%------------------------------------------------------------------------
\section{Experiments}
\label{sec:exp}

Experiments.

>>>>

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{booktabs}

@@

%------------------------------------------------------------------------
\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=\textwidth]{../x4result.pdf}
    \end{center}
    \caption{Comparison of image quality between our method and the bicubic method.}
    \label{yolov3}
\end{figure*}

\section{Experimental Evaluation}
\label{sec:exp}
In this section, we present the experimental evaluation of our proposed approach for image super-resolution. We first describe the experimental setup, including the datasets used, the hardware and software configurations, and the evaluation metrics. We then present the results of our experiments, which demonstrate the effectiveness of our approach.

\subsection{Experimental Setup}

\subsubsection{Datasets}
In this work, we use two widely used datasets in the field of super-resolution: DIV2K\cite{div2k} and LSDIR\cite{lilsdir} as the training datasets.

The DIV2K dataset is a widely used dataset for super-resolution tasks. It comprises 1000 images characterized by significantly higher resolution than those of the commonly referenced datasets. All the 1000 images are 2K resolution, that is they have 2K pixels on at least one of the axes(vertical or horizontal). All the images were processed using the same tools to $\times2$, $\times3$, and $\times4$ downscaling factors. The images cover a variety of scenes, including landscapes, portraits, and still-life compositions.

The LSDIR dataset proposes a large scale dataset for image restoration. It contains 84,991 high-quality training images and 250 validation images from the whole validation set. The dataset provides both high and low-resolution images for $\times2$, $\times3$, and $\times4$ downscaling factors.

For evaluation, we used Set5, Set14, BSDS100, and Urban100 datasets to verify the effectiveness of the image recovery quality of our method. These datasets contain a diverse range of images with different levels of complexity, making them suitable for evaluating the performance of super-resolution algorithms.

We evaluated our approach's computational efficiency using DIV2K dataset.

\subsubsection{Hardware and Software Configurations}
All experiments were conducted on a workstation equipped with an NVIDIA GeForce RTX 3070 GPU, 512GB of RAM, and an Intel(R) Xeon(R) Gold 6230R CPU. We used the Pytorch framework (version 1.13.0) for implementing and training our models. We used the Adam optimizer with a learning rate of 1e-5 and a batch size of 16 for training. We trained the model for 300 epochs on the DIV2K dataset and 300 epochs on the LSDIR dataset.

\subsubsection{Evaluation Metrics}
To evaluate the performance of our algorithm, we used two commonly used evaluation metrics: peak signal-to-noise ratio (PSNR) and structural similarity index (SSIM). Additionally, we report the validation time, test time, average time, model parameters, floating-point operations (FLOPs), activation volume, and memory consumption associated with our proposed algorithm. These metrics provide a comprehensive evaluation of our approach's effectiveness and computational efficiency.
\begin{table}[t]
  \centering
  \caption{Results of our computational efficiency on DIV2K dataset.}
  \resizebox{\linewidth}{!}{
  \begin{tabular}{cccccc}
    \toprule
    Ave Time[ms] & Params[M] &FLOPs[G] &Acts [M] & Mem[M] &Conv\\
    \midrule
    40.84&0.616&38.63&133.57&944.91&64\\
    \bottomrule
  \end{tabular}
  }
  \label{tab-runtime}
\end{table}

\begin{table}[t]
    \caption{Compared with the bicubic method, our method can effectively improve image quality.}
    \resizebox{\columnwidth}{!}
    {
        \begin{tabular}{|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100  \bigstrut\\
    \cline{4-7}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM  \\
        \hline
        Bicubic & \multirow{2}[2]{*}{×2} & -     & 28.42/0.8104 & 26.00/0.7027 & 25.96/0.6675 & 23.14/0.6577  \\
        PRFDN (Ours) &       & 616K  & 30.20/0.8632 & 26.84/0.7444 & 26.24/0.7115 & 24.66/0.7662 \\
        \hline
        \end{tabular}%
    }
    \label{tab-quality}
\end{table}%
\subsection{Results}
Our approach achieves high PSNR and SSIM. Compared with the bicubic interpolation algorithm, we are able to get 4.3\% and 8.9\% improvement of PSNR and SSIM respectively. The results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images. Table \ref{table-result} displays the quality performance of our approach methods on different datasets compared to other methods by PSNR and SSIM scores.

Furthermore, our approach achieves fast validation and test times, indicating its superior computational efficiency. Table \ref{table-time} presents the performance of our proposed approach and state-of-the-art methods on the DIV2K dataset in terms of validation time, test time, average time, and memory consumption. Our approach achieves a fast average time with a result of 40.84ms on the DIV2K dataset. The test time and validation time are also significantly low. Specifically, our approach achieved a low test time of 33.33ms and a validation time of 48.35ms. Our approach's memory consumption is 944.91 MB.

\subsection{Discussion}
The results presented in this paper demonstrate the effectiveness and computational efficiency of our proposed super-resolution algorithm on two challenging datasets. Our method achieved high PSNR and SSIM scores on both DIV2K and LSDIR datasets, indicating that our approach can significantly enhance image resolution while preserving image details and textures.

Furthermore, our method showed remarkable computational efficiency, achieving a fast average time and low memory consumption compared to the baseline method. This is a crucial aspect for practical applications that require real-time super-resolution processing, such as video streaming and surveillance.

While our approach showed promising results, some limitations and potential directions for future research should be noted. We only trained our method on two datasets with a limited number of images, which could be investigated in future work.

### 2023-04-05 NTIRE 2023 RTSR Paper/PaperForReview.tex
x4 exp & x2 exp(未完成)

>>>>

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=\textwidth]{../x4result.pdf}
    \end{center}
    \caption{Comparison of image quality between our method and the bicubic method.}
    \label{yolov3}
\end{figure*}

\section{Experimental Evaluation}
In this section, we evaluate our our proposed image super-resolution algorithm through various experiments. The experimental setting is first described, including experiment datasets, hardware and software configurations, and assessment measures. Besides, we present the results of our experiments, and compare our method with other existing study to demonstrate the success of our approach.

\subsection{Experimental Setup}

\subsubsection{Datasets}
We used Set5, Set14, BSDS100, and Urban100 datasets to verify the effectiveness of the image recovery quality of our method. These datasets contain a diverse range of images with different levels of complexity, making them suitable for evaluating the performance of super-resolution algorithms.

We evaluated our approach's computational efficiency using some widely used datasets in the field of super-resolution: DIV2K\cite{div2k}, LSDIR\cite{lilsdir}.

The DIV2K dataset is a widely used dataset for super-resolution tasks. It comprises 1000 images characterized by significantly higher resolution than those of the commonly referenced datasets. All the 1000 images are 2K resolution, that is they have 2K pixels on at least one of the axes(vertical or horizontal). All the images were processed using the same tools to $\times2$, $\times3$, and $\times4$ downscaling factors. The images cover a variety of scenes, including landscapes, portraits, and still-life compositions.

The LSDIR dataset proposes a large scale dataset for image restoration. It contains 84,991 high-quality training images and 250 validation images from the whole validation set. The dataset provides both high and low-resolution images for $\times2$, $\times3$, and $\times4$ downscaling factors.

The others

\subsubsection{Hardware and Software Configurations}
We conducted all experiments on the laptop with an NVIDIA GeForce RTX 3070 GPU, 512GB of RAM, and an Intel(R) Xeon(R) Gold 6230R CPU in the PyTorch environment (version 1.13.0). When training the model, we used the Adam optimizer with a learning rate of 1e-5 and a batch size of 16. We trained the model on the DIV2K dataset for 300 epochs and the LSDIR dataset for 300 epochs.

\subsubsection{Evaluation Metrics}
In the experiment, Peak signal-to-noise ratio (PSNR) and structural similarity index (SSIM), two common evaluation metrics, are used to evalute the performance of our algorithm.  
Additionally, we report the validation time, test time, average time, model parameters, floating-point operations (FLOPs), activation volume, and memory consumption associated with our proposed algorithm. These metrics provide a comprehensive evaluation of effectiveness and computational efficiency about our method.

\subsection{Results}
Our approach has performed well through a series of experiments. The method increases the PSNR and SSIM scores by 10\% and 15\% respectively, compared to the bicubic interpolation algorithm. These results demonstrate the effectiveness of our proposed super-resolution algorithm on high-resolution images. Table \ref{table-time} shows the PSNR and SSIM scores of our method compared to some existing methods on different datasets.

Additionally, our method achieves fast test and validation times, demonstrating its superior computational efficiency. On the DIV2K dataset, Table \ref{table-time} shows the performance of our proposed approach on the DIV2K dataset in terms of validation time, test time, average time, and memory usage compared with state-of-the-art methods. Our method achieves a fast average time with 10000ms on the DIV2K dataset. Both the test time and the validation time are particularly low. Specifically, our approach achieved a low validation time of 10000ms. The memory consumption of our approach is 10000MB.

\begin{table}[h]
  \centering
  \caption{Results.   Ours is better.}
  \resizebox{\linewidth}{!}{
  \begin{tabular}{lccccc}
    \toprule
    Ave Time[ms] & Params[M] &FLOPs[G] &Acts [M] & Mem[M] &Conv\\
    \midrule
    25.97&00.402&25.23&81.88&344.51&39\\
    \bottomrule
  \end{tabular}
  }
  \label{tab:example}
\end{table}

% Table generated by Excel2LaTeX from sheet 'Sheet1'

\begin{table}[htbp]
    \resizebox{\columnwidth}{!}
    {
        \begin{tabular}{|c|c|c|c|c|c|c|c|}
        \hline
        \multirow{2}{*}{Method} & \multirow{2}{*}{Scale} & \multirow{2}{*}{Params} & Set5  & Set14 & BSD100 & Urban100 & Manga109 \bigstrut\\
    \cline{4-8}          &       &       & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM & PSNR/SSIM \bigstrut\\
        \hline
        Bicubic & \multirow{14}[2]{*}{×2} & -     & 33.66/0.9299 & 30.24/0.8688 & 29.56/0.8431 & 26.88/0.8403 & 30.80/0.9339 \bigstrut[t]\\
        SRCNN[5] &       & 8K    & 36.66/0.9542 & 32.45/0.9067 & 31.36/0.8879 & 29.50/0.8946 & 35.60/0.9663 \\
        FSRCNN[6] &       & 13K   & 37.00/0.9558 & 32.63/0.9088 & 31.53/0.8920 & 29.88/0.9020 & 36.67/0.9710 \\
        VDSR[19][13] &       & 666K  & 37.53/0.9587 & 33.03/0.9124 & 31.90/0.8960 & 30.76/0.9140 & 37.22/0.9750 \\
        DRCN[32][14] &       & 1774K & 37.63/0.9588 & 33.04/0.9118 & 31.85/0.8942 & 30.75/0.9133 & 37.55/0.9732 \\
        DRRN[30] &       & 298K  & 37.74/0.9591 & 33.23/0.9136 & 32.05/0.8973 & 31.23/0.9188 & 37.88/0.9749 \\
        MemNet[35] &       & 678K  & 37.78/0.9597 & 33.28/0.9142 & 32.08/0.8978 & 31.31/0.9195 & 37.72/0.9740 \\
        IDN[12] &       & 553K  & 37.83/0.9600 & 33.30/0.9148 & 32.08/0.8985 & 31.27/0.9196 & 38.01/0.9749 \\
        SRMDNF[42] &       & 1511K & 37.79/0.9601 & 33.32/0.9159 & 32.05/0.8985 & 31.33/0.9204 & 38.07/0.9761 \\
        CARN[1] &       & 1592K & 37.76/0.9590 & 33.52/0.9166 & 32.09/0.8978 & 31.92/0.9256 & 38.36/0.9765 \\
        LAPAR-A[18] &       & 548k  & 38.01/0.9605 & 33.62/0.9183 & 32.19/0.8999 & 32.10/0.9283 & 38.67/0.9772 \\
        IMDN[11] &       & 694K  & 38.00/0.9605 & 33.63/0.9177 & 32.19/0.8996 & 32.17/0.9283 & 38.88/0.9774 \\
        RFDN[24] &       & 534K  & 38.05/0.9606 & 33.68/0.9184 & 32.16/0.8994 & 32.12/0.9278 & 38.88/0.9773 \\
        HNCT (Ours) &       & 356K  & 38.08/0.9608 & 33.65/0.9182 & 32.22/0.9001 & 32.22/0.9294 & 38.87/0.9774 \bigstrut[b]\\
        \hline
        \end{tabular}%
    }
\end{table}%

\subsection{Discussion}
Our super-resoluton algorithm performed well on two challenging datasets with great effectiveness and computational efficiency. On both the DIV2K and LSDIR datasets, our method achieved high PSNR and SSIM scores, indicating that our approach can greatly improve image resolution while preserving image features and textures.

Additionally,when compared to the baseline method, our method demonstrated outstanding computing efficiency, reaching a rapid average time and low memory consumption, which is crucial for real-world applications requiring real-time super-resolution processing, such as video streaming and surveillance.

Although our study achieved encouraging results, some limitations and potential future research approaches should be addressed. We only tested our algorithm on two datasets with a limited number of images, which might be expanded upon in future research.
